\documentclass{report}
\usepackage{graphicx}

\setcounter{secnumdepth}{3}

\setcounter{tocdepth}{3}

\begin{document}

\title{Time Stamper}
\author{Erik Ahlberg}

\maketitle

\tableofcontents

\newpage

\chapter{Introduction}
This document contains the top level description of the Time Stamper application. If you want to get an overall understanding of this project, you are in the right place. The introductory chapters explain the main intent and purpose of this project, painting the broader picture to why things are done the way they are.

The second part dwelves into the business logic of the application. It explains the main services and properties of the application as well as the problem it intends to solve for the customer.

The third and last section of this document describes the overall system design responsible for implementing the desired business logic.

\section{Intent}
The main intent of this project is to acquire new, as well as hone existing, software development skills. It shall ultimately serve its developers in the sense that it is not the end product that is the goal, it is the journey. Each part of the project shall try as far as possible to adhere to the industries best practices, w.r.t. quality and efficiency. The reason is to create a development process and environment that each project member can learn and draw experience from. When the project is over, each member should have acquired a set of new skills and experiences that it can show for in other work related contexts.

\section{Purpose - Business Domain}
Describe the purpose with this project in terms of its business value.

\section{Scope}
Describe the limitations and scope of this project as well as this document.

\chapter{Business Services}
Short summary of the main business values and market focus.

\section{Time Stamping}
Description of the stamping function.

\subsection{Trends}
Description of the trends of work hours function.

\subsection{Future Schedule}
Description of the work schedule function.

\subsection{Income Calculator}
Description of the income calculator function.

\chapter{System Design}
Overall summary of the total system meant to produce the previously described business services.

\section{System Architecture}
Overall summary of the system components that comprise the complete architecture for the system.

\subsection{System Components}
In detail description of the components comprising the complete system, and their roles within it.

\subsubsection{Component Interactions}
In detail descritpion of the component interactions, i.e. their communication patterns, with each other.

\subsection{Client Front-End}
In detail description of the front-end applicaiton.

\subsection{Back-End Services}
In detail description of the back-end application.

\chapter{System Requirements}
Collection of necessary system requirements.

\end{document}

